### 2015-01-10 paper/Content/solution.tex
App prototype testing

@@

The MVP pattern can be applied to \emph{Fragments} the same way as it is described above for \emph{Activities}. Presenters of \emph{Fragment} objects most likely share their model with either other \emph{Fragments} and other \emph{Activities}. An example of this was implemented in the \texttt{WeatherDetailsActivity} of the app prototype, which shows the weather data for a selected location. The part of the view showing temperature and wind information was extracted into a separate \emph{Fragment} with its own presenter implementation. Clicking on the \emph{Refresh} button causes the presenter of the activity to instruct the model to fetch updated weather data from \emph{openweathermap.org}. When this data is available, the model notifies all registered observers -- in this case the presenter of the activity and the presenter of the fragment. Both presenters go back to the corresponding view objects and cause the updated data to be displayed.

@@

>>>>

\subsection{App Structure}

@@

The MVP pattern can be applied to \emph{Fragments} the same way as it is described above for \emph{Activities}. Presenters of \emph{Fragment} objects most likely share their model with other \emph{Fragments} and other \emph{Activities}. An example of this was implemented in the \texttt{WeatherDetailsActivity} of the app prototype, which shows the weather data for a selected location. The part of the view showing temperature and wind information was extracted into a separate \emph{Fragment} with its own presenter implementation. Clicking on the \emph{Refresh} button causes the presenter of the activity to instruct the model to fetch updated weather data from \emph{openweathermap.org}. When this data is available, the model notifies all registered observers -- in this case the presenter of the activity and the presenter of the fragment. Both presenters go back to the corresponding view objects and cause the updated data to be displayed.

@@

\subsection{Testing the App}

As mentioned before in section \ref{sec:research}, a key benefit of an MVP architecture is the increased testability of the software.
To demonstrate this ability, some tests for the app prototype were created using the testing capabilities of the Android SDK -- the Android testing framework:

\textbf{Activity Unit Test}:
An activity object will be created in an isolated environment. This means that, except from the tested activity object, every other component, like the application itself, is replaced by a mock implementation. This includes the presenter object as well. Using such a mock presenter implementation allows to easily test the interaction between an activity and its presenter.
An example would be the simulation of a button click and the assertion, if the presenter object was called correctly.
Without having MVP in place, the isolation of an activity object would be way more complicated or may even not be possible at all.

\textbf{Model Unit Test}
As the model objects of the app prototype have no dependency to any Android related component, they are very good for being tested through unit tests. As described for activities above, the model object will be created in an isolated environment with a mock presenter implementation.
